Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-14 paper/paper.tex
pass on section 4

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test files. Dashed
    rectangle under column ``type-in-all'' shows the tests used for
    test transplantation whereas the rectangle under column
    ``no-fail-in-all''---a subset of the ``type-in-all'' tests---shows
    the tests used in cross-engine differential
    testing.}
  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
    \midrule
    \jsc & \cite{jsc2018repo} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
    \veight{} & \cite{v82018repo} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
    %\chakra & \cite{chakra2018repo}\\
    \hermes & \cite{hermes2020repo} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{} \\
    \midrule
    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\
    \jerry{} & \cite{jerryscript2018repo} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
    Babel & \cite{babel2020repo} & \babelOriginal{} & \babelPassInPar{} & \babelCompileAll{} & \babelNoFailAll{} \\
    BlogEngine.NET & \cite{blogEngineNet2020repo} & \blogEngineNetOriginal{} & \blogEngineNetPassInPar{} & \blogEngineNetCompileAll{} & \blogEngineNetNoFailAll{} \\
    \midrule
    %GitHub Projects & - & 494,394 & - & - & - \\
    %\midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule
  \end{tabular}
\end{table}

@@

Column ``type-in-all'' shows the number of test cases whose executions
do not throw dynamic type errors in any of the engines because of an
undefined variable or property.  These cases were captured by looking
for the presence of \CodeIn{ReferenceError} and \CodeIn{TypeError} on
the output. A \CodeIn{ReferenceError} (respectively,
\CodeIn{TypeError}) is raised when test execution attempts to access
an undefined variable (respectively, property of an object). We
discarded those tests to avoid noise in the experiments as they
indicate some missing feature in the implementation of the engine as
opposed to bugs. For example, some tests use non-portable names
(\eg{}, \jsc's \CodeIn{drainMicrotasks()} and \smonkey{}'s
\CodeIn{Error.lineNumber}) or use functions that, albeit part of the
spec, not all engines currently support. Similarly, the \chakra
project does not use common assertions available used in JS program,
which other JS engines support. Instead, it uses its own testing
framework, WScript. In such cases, we are unable to reproduce the
\chakra unit tests in other engines---it raises a
\CodeIn{ReferenceError}. Also, updating the other engines to use
WScript would require a non-trivial manual effort. This is why \chakra
does not appear in Table~\ref{tab:test-suites}. For the evaluation of
test transplantation, we used the
\totalTestFilesForTestTransplantation{} tests included in the dashed
rectangle under column ``type-in-all'', \ie{}, all tests under that
column but the Test262 tests. We did not consider tests from the
conformance suite as they are more likely to indicate missing features
as opposed to bugs. In addition, engine developers have access to
these tests and are encouraged to run them.

Column ``no-fail-in-all'' shows the tests for which all engines
pass. The set of tests in this column is a subset of the
``type-in-all'' test set. The tests in this set are as fuzzing seeds
in the evaluation of differential testing. The guarantee that they
pass in all engines assures that, if discrepancies occur, they are
related to the changes in the input as opposed to the original cause
of failure.
\Fix{It is worth noting that we also did not include the tests
from \hermes\ in the table because, as the reader shall see in
Table~\ref{tab:test262}, \hermes presents a very low adherence to the
Test262 conformance suite. If we decided to keep \hermes, considering
only the number of passing tests in all engines (the
``no-fail-in-all'' column), it would significantly reduce our amount of test files.}
$\leftarrow$\Breno{Haven't we decided that Hermes should be removed from Table 3?
If yes, maybe this explanation will only create confusing.}
\Mar{Not sure if I understood the conclusion. Do you mean the total amount of test
  (also from other suites)? Why?}

@@

\lbrack{}Additional cleansing\rbrack{}~We noticed that some of the
tests we found depend on external libraries, which not all selected
engines support. We decided to discard those. For example, many tests
we found were based on Node.js~\cite{node} which
%\Mar{@Igor, is this the reason?  Please, confirm$\rightarrow$}
%\Igor{yes, it is. Some Node internal features are
%not included in the JS engine, including some keywords (ie. require, module).
%In addiction, a project with nodejs require a package.json with a lot of external dependencies.}
require libraries to be
installed before running the test and different tests require
different sets of libraries. Also, as already mentioned, we did not
consider tests from the \chakra{} repository because they depend on
non-portable objects.  Finally, note that the number of tests in
\veight\ is low; that happens because \veight{} uses many tests from
Mozilla and \jsc; we discarded those to avoid repetition and to give
credit where it is due.

\lbrack{}Test Harness\rbrack{}~It is also worth mentioning that some
engines uses a custom shell to run tests, including a harness with
specific assertions. For example, tests provided by Mozilla contain a lot
of custom functions (\eg\ assertThrowsInstanceOf, assertEqArray, getPromiseResult)
and those are included in the shell to make the test run correctly.
For that, we needed to make minor changes in the testing infrastructure to be able
to run the tests uniformly across all engines. More precisely, we
needed to mock non-portable functions, which are only available in
certain engines. Since we had to transplant more than 40k test files,
we tried to mock the minimum amount of code possible to make the test
file work in the other engine.\Mar{This seems a different problem
  (tests without assertions). I did not understand how this is related
  to portability?}\Igor{A test is a simple JS file input.
  Some tests are not well-defined.}  For instance, if a test had a statement such as
\texttt{print(1==1);} we manually refactored that statement to
\texttt{assert(1==1)} which should throw an assertion violation if the condition returns false.
If the change would require more substantial manual work, we opted to discard the test instead. Overall,
we may have manually refactored more than a thousand test files.

\lbrack{}Dedup\rbrack{}~\Fix{Explain what we did to avoid
  dups. Consider moving to the the sentence ``Finally, note that the number of tests in V8''}

@@

\subsection{Characterization of Test Suites}

\Fix{...add and discuss histograms}

@@

>>>>

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test files. Dashed
    rectangle under column ``type-in-all'' shows the tests used for
    test transplantation whereas the rectangle under column
    ``no-fail-in-all''---a subset of the ``type-in-all'' tests---shows
    the tests used in cross-engine differential
    testing.}
  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
    \midrule
    \jsc & \cite{jsc2018repo} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
    \veight{} & \cite{v82018repo} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
    %\chakra & \cite{chakra2018repo}\\
    \hermes & \cite{hermes2020repo} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{} \\
    \midrule
    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\
    \jerry{} & \cite{jerryscript2018repo} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{} & \tinyNoFailAll{}\\
    Babel & \cite{babel2020repo} & \babelOriginal{} & \babelPassInPar{} & \babelCompileAll{} & \babelNoFailAll{} \\
    BlogEngine.NET & \cite{blogEngineNet2020repo} & \blogEngineNetOriginal{} & \blogEngineNetPassInPar{} & \blogEngineNetCompileAll{}\markbottomright{c1} & \blogEngineNetNoFailAll{}\markbottomright{c2} \\
    \midrule
    %GitHub Projects & - & 494,394 & - & - & - \\
    %\midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule
  \end{tabular}
\end{table}

@@

Column ``type-in-all'' shows the number of test cases whose executions
do not throw dynamic type errors in any of the engines because of an
undefined variable or property.  These cases were captured by looking
for the presence of \CodeIn{ReferenceError} and \CodeIn{TypeError} on
the output. A \CodeIn{ReferenceError} (respectively,
\CodeIn{TypeError}) is raised when test execution attempts to access
an undefined variable (respectively, property of an object). We
discarded those tests to avoid noise in the experiments as they
indicate some missing feature in the implementation of the engine as
opposed to bugs. For example, some tests use non-portable names
(\eg{}, \jsc's \CodeIn{drainMicrotasks()} and \smonkey{}'s
\CodeIn{Error.lineNumber}) or use functions that, albeit part of the
spec, not all engines currently support. Similarly, the \chakra
project does not use common assertions available used in JS program,
which other JS engines support. Instead, it uses its own testing
framework, WScript. In such cases, we are unable to reproduce the
\chakra unit tests in other engines---it raises a
\CodeIn{ReferenceError}. Also, updating the other engines to use
WScript would require a non-trivial manual effort. This is why \chakra
does not appear in Table~\ref{tab:test-suites}. For the evaluation of
test transplantation, we used the
\totalTestFilesForTestTransplantation{} tests included in the dashed
rectangle under column ``type-in-all'', \ie{}, all tests under that
column but the Test262 tests. We did not consider tests from the
conformance suite as they are more likely to indicate missing features
as opposed to bugs. In addition, engine developers have access to
these tests and are encouraged to run them.
Column ``no-fail-in-all'' shows the tests for which all engines
pass. The tests in this set are used as fuzzing seeds in the
evaluation of differential testing. The guarantee that tests pass in
all engines assures that discrepancies are related to the changes in
the input produced by fuzzers.

@@

\lbrack{}Cleansing\rbrack{}~We noticed that some of the tests we found
depend on external libraries, which not all selected engines
support. We decided to discard those. For example, we found many tests
based on Node.js~\cite{node} that
%\Mar{@Igor, is this the reason?  Please, confirm$\rightarrow$}
%\Igor{yes, it is. Some Node internal features are not included in the
%JS engine, including some keywords (ie. require, module).  In
%addiction, a project with nodejs require a package.json with a lot of
%external dependencies.}
require libraries to be installed before running the test and
different tests require different sets of libraries. Supporting those
tests would require an extra setup step and would slow down the
execution of our experiments. Also, as already mentioned, we did not
consider tests from the \chakra{} repository because they depend on
non-portable objects.

\lbrack{}Test Harness\rbrack{}~We noticed that some engines use a
custom shell to run tests, including a harness with specific
assertions. For example, tests provided by Mozilla contain a lot of
custom functions (\eg{}, \CodeIn{assertThrowsInstanceOf},
\CodeIn{assertEqArray}, and \CodeIn{getPromiseResult}) and those are
included in the shell to make the test run correctly.  For that, we
needed to make minor changes in the testing infrastructure to be able
to run the tests uniformly across all engines. More precisely, we
needed to mock non-portable functions, which are only available in
certain engines. Since we had to transplant more than 40k test files,
we tried to mock the minimum amount of code possible to make the test
file work in the other engine. For instance, if a test had a statement
such as \texttt{print(1==1);} we manually refactored that statement to
\texttt{assert(1==1)} which should throw an assertion violation if the
condition returns false.  If we found the change would require
substantial manual work, we opted to discard the test instead.

%Overall, we may have manually refactored more than a thousand test files.

%% \Mar{This seems a different problem
%%   (tests without assertions). I did not understand how this is related
%%   to portability?}\Igor{A test is a simple JS file input.  Some tests
%%   are not well-defined.}

\lbrack{}Dedup\rbrack{}~The number of tests in \veight\ is low because
we dicarded duplicate tests with Mozilla and \jsc. The rationale is to
avoid inflating results and giving credit where it is due. We also
wrote a script that compares each pair of tests from different suites
for similarity. We did not find identical tests, although it is
possible there are equivalent tests modulo renaming.

%\Fix{Explain what we did to avoid dups. Consider
%  moving to the the sentence ``Finally, note that the number of tests
%  in V8''}

@@

%% \subsection{Characterization of Test Suites}

%% To provide a brief overview of the test suites and understand if the engines
%% have specific testing purposes, we investigated the most common
%% objects and functions that each one of the JS engines employ.
%% To achieve this goal, we started by filtering out many non-relevant source
%% code statements available on the test suites. We started by removing JS language constructs (such as \texttt{if}, \texttt{for}, and \texttt{var}). We then removed
%% special characters (such as parentheses, mathematical symbols, and semicolons).
%% For the remaining source code constructs, we search for the ``.'' character, which
%% indicates a function call. We then stored the function and the object that host
%% that function.  By manually analyzing this data, we noted many general purpose
%% functions, that do not provide any hint on the kind of behavior the engine is
%% more likely to test (such as \texttt{console.log}). We also removed these
%% general purpose functions. The remaining object/functions are shown at
%% Figure~\ref{fig:histograms}.

%% \begin{figure}[thp]
%% \begin{center}
%% $
%% \begin{array}{cc}
%% Charka & Duktape \\
%% \includegraphics[width=.5\textwidth, clip, trim= 0px 35px 10px 0px]{figs/hist/chakra.pdf} &
%% \includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/duktape.pdf} \\
%% Hermes & JerryJS \\
%% \includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/hermes.pdf} &
%% \includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/jerryJS.pdf} \\
%% JSI & Test262 \\
%% \includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/jsi.pdf} &
%% \includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/test262.pdf} \\
%% TinyJS & V8 \\
%% \includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/tinyJS.pdf} &
%% \includegraphics[width=.5\textwidth, clip,trim= 0px 35px 10px 0px]{figs/hist/v8.pdf} \\
%% \end{array}
%% $
%% \end{center}
%% \caption{histograms.}
%% \label{fig:histograms}
%% \end{figure}

@@

\Mar{moved from Section 4. check if useful. $\rightarrow$}
\Fix{It is worth noting that we also
  did not include the tests from \hermes\ in the table because, as the
  reader shall see in Table~\ref{tab:test262}, \hermes presents a very
  low adherence to the Test262 conformance suite. If we decided to
  keep \hermes, considering only the number of passing tests in all
  engines (the ``no-fail-in-all'' column), it would significantly
  reduce our amount of test files.}  $\leftarrow$\Breno{Haven't we
  decided that Hermes should be removed from Table 3?  If yes, maybe
  this explanation will only create confusing.}  \Mar{Not sure if I
  understood the conclusion. Do you mean the total amount of test
  (also from other suites)? Why?}
